Fuel switch, savings, electrification - Decarbonisation in industry OR Pathways to Carbon Neutral Industrial Sectors: Integrated Modelling Approach with High Level of Detail for End-use Processes OR Decarbonization options in industry and conceptual model of industry in the integrated energy system

### 2018-01-21 article.tex
status Sunday 21.01

\autoref{heatmapagri}, \autoref{heatmapprod}, \autoref{heatmapserv} provide an indication on the fuel-use for the different industrial processes. The production data are reported as a single aggregated group; for the breakdown, please refer to (APPENDIX).

@@

\begin{figure}[H]
\centering
\includegraphics[width=\linewidth]{Img/dan_ind/heatmap_serv.png}
\caption{Breakdown of energy consumption by end-use and fuel in services\cite{VM2015}}
\label{heatmapserv} 
\end{figure}

@@

In production, there is a high diversity of end-use while the role of gas as a fuel is predominant. 
Space heating and transport dominate the total energy use in the service sector. While most space heat already supplied by district heat, natural gas is the second.

@@

@@

\includegraphics[scale=0.36]{img/DK_DH_Balmorel_areas2.png}
\caption District Heat Areas in Denmark. Sources: \cite{kortforsyningen2017,forsyningsomraade2017}}

@@

\includegraphics[scale=0.36]{img/DK_DH_Balmorel_areas2_DH_share_PHL.png}\\
\caption{Low process heat demand supplied by district heat. Own calulations based on: \cite{kortforsyningen2017,virk2017,Buhler2017,Petrovic2014,VM2015,StatisticsDenmark2016}}

A similar approach is applied to derive the demand profiles per area. For each area, one process heat and one space heat profile is generated based on the shares the main industry groups Service, Production single, Production double and Production triple have in the industrial process and space heat demand of the area.

>>>>

\iffalse
\autoref{heatmapagri}, \autoref{heatmapprod}, \autoref{heatmapserv} provide an indication on the fuel-use for the different industrial processes. The production data are reported as a single aggregated group; for the breakdown, please refer to (APPENDIX).

@@

\begin{figure}[H]
\centering
\includegraphics[width=\linewidth]{Img/dan_ind/heatmap_serv.png}
\caption{Breakdown of energy consumption by end-use and fuel in services\cite{VM2015}}
\label{heatmapserv} 
\end{figure}
\fi

@@

%top up with data
In production, there is a high diversity of end-use while the role of gas as a fuel is predominant. 
Space heating and transport dominate the total energy use in the service sector. While most space heat already supplied by district heat, natural gas is the second.

@@

The energy system model Balmorel considers the industry sector only as a part of the total heat and electricity consumption within the optimisation. Thus all the end use processes and fuel specification, previously described, are currently neglected. The black dotted line in \autoref{ensyst} represents the boundaries in the current version of Balmorel, where the industry is considered simply as part of the total energy demand .

\begin{figure}[H]
\centering
\includegraphics[width=\linewidth]{Img/ind_model/IndustryEnergyFlowchart.pdf}
\caption{Schematic of industry sector representation in Balmorel}
\label{ensyst} 
\end{figure}

\autoref{ensyst} shows the schematic of the novel structure proposed, to consider the diverse and rich characteristics of the industry sector in the energy system model. The same structure is applied for each of the 57 sectors considered.

The first addition introduced concerns the commodities part of the energy demand: electricity, fuels and heat.
The electricity demand now satisfies, in every single sector, the demand of the single end-uses. This addition facilitates the investigation of decarbonisation options (e.g. savings) at a later stage, as the new options can be applied directly to each end use (\textbf{maybe rewrite, the point here is that the more disaggregated is the consumption, the easier will be to investigate other options to satisfy the demand of decrease the demand}). 
Furthermore, electricity can be either be imported by the grid, or it can be self-produced using small plants. It can also be used to run heat pumps and satisfy the heat demand, or "elevate" the quality of heat, for peculiar processes. 
Heat, previously considered only as district heat demand, now includes three temperature levels: space heating, process heat low temperature and process heat high temperature processes.

Electricity, heat and fuels are considered as energy inputs for the end-use processes in industry. 
Fuels can also be used as fuel-feedstock directly for the industrial processes in the model to better represent reality. 
Heat is separated as space and process heat and distinguished between different temperature levels. In this way, it can be supplied by different sources and technologies.
Specific electricity profiles for the industrial sectors are the basis for the demand profiles fed into the model. Space heating for the industry sector can be supplied by district heating, but can also be self-generated, using the fuel in a plant on site to generate electricity and heat.

@@

\iffalse
\includegraphics[scale=0.36]{img/DK_DH_Balmorel_areas2.png}
\caption{ District Heat Areas in Denmark. Sources: \cite{kortforsyningen2017,forsyningsomraade2017}}

@@

\includegraphics[scale=0.36]{img/DK_DH_Balmorel_areas2_DH_share_PHL.png}\\
\caption{Low process heat demand supplied by district heat. Own calulations based on: \cite{kortforsyningen2017,virk2017,Buhler2017,Petrovic2014,VM2015,StatisticsDenmark2016}}
\fi
A similar approach is applied to derive the demand profiles per area. For each area, one process heat and one space heat profile is generated based on the shares the main industry groups Service, Production single, Production double and Production triple have in the industrial process and space heat demand of the area.
